The Three-HITs Theorem

### 2017-03-27 Paper/Paper.tex
Fix affiliation and acknowledgements.

% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{The Three-HITs Theorem\footnote{This work was partially supported by COST Action CA15123.}}
\titlerunning{The Three-HITs Theorem} %optional, in case that the title is too long; the running title should fit into the top page column

%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
\author[1]{Andrej Bauer}
\author[2]{Niels van der Weide}
\affil[1]{Faculty of Mathematics and Physics, University of Ljubljana, Ljubljana, Slovenia\\
  \texttt{Andrej.Bauer@andrej.com}}
\affil[2]{Department of Computer Science, Radboud University, Nijmegen, The Netherlands\\
  \texttt{nweide@cs.ru.nl}}
\authorrunning{A.\ Bauer and N.\ van der Weide} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'

>>>>

% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{The Three-HITs Theorem}
\titlerunning{The Three-HITs Theorem} %optional, in case that the title is too long; the running title should fit into the top page column

%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
\author[1]{Andrej Bauer\thanks{
The author acknowledges the financial support from the Slovenian Research Agency (research core funding No.~P1-0294) at Institute of Mathematics, Physics and Mechanics, Ljubljana, Slovenia. This material is based upon work supported by the Air Force Office of Scientific Research, Air Force Materiel Command, USAF under Award No.~FA9550-14-1-0096.}}
\author[2]{Niels van der Weide\thanks{This work was partially supported by EU COST Action Eutypes (CA15123).}}
\affil[1]{University of Ljubljana, Slovenia\\
  \texttt{Andrej.Bauer@andrej.com}}
\affil[2]{Department of Computer Science, Radboud University, Nijmegen, The Netherlands\\
  \texttt{nweide@cs.ru.nl}}
\authorrunning{A.\ Bauer and N.\ van der Weide} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'
